
---
title: "Ad Strategy for EV Charging Stations. "
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(plotly)
library(dplyr)

# Simulación de carga de datos y gráficos
source("scripts/univariate_analysis.R", local = TRUE)
source("scripts/bivariate_complete.R", local = TRUE)
source("scripts/multivariate_analysis.R", local = TRUE)

load_data <- univariate_analysis$load_data
data <- load_data(file.path(getwd(), "datasources", "ev_charging_patterns.csv"))

# Gráficos univariados
univariate_plot1 <- ggplotly(univariate_analysis$generate_user_type_plot(data))
univariate_plot2 <- ggplotly(univariate_analysis$generate_day_of_week_plot(data))
univariate_plot3 <- ggplotly(univariate_analysis$generate_charging_station_location_plot(data))
univariate_plot4 <- ggplotly(univariate_analysis$generate_end_hour_plot(data))
univariate_plot5 <- ggplotly(univariate_analysis$generate_charger_type_plot(data))

# Gráficos bivariados
bivariate_plot1 <- ggplotly(bivariate_complete$generate_user_type_end_time_plot(data))
bivariate_plot2 <- ggplotly(bivariate_complete$generate_user_type_location_plot(data))
bivariate_plot3 <- ggplotly(bivariate_complete$generate_charger_type_day_of_week_plot(data))
bivariate_plot4 <- ggplotly(bivariate_complete$generate_end_time_day_of_week_plot(data))

# Gráficos multivariados
multivariate_plot <- ggplotly(multivariate_analysis$generate_multivariate_plot(data))
```

Univariate
======================================================

### Univariate Analysis: User Type
```{r, echo=FALSE}
univariate_plot1
```

### Univariate Analysis: Day of Week
```{r, echo=FALSE}
univariate_plot2
```

### Univariate Analysis: Charging Station Location
```{r, echo=FALSE}
univariate_plot3
```

### Univariate Analysis: End Hour
```{r, echo=FALSE}
univariate_plot4
```

### Univariate Analysis: Charger Type
```{r, echo=FALSE}
univariate_plot5
```

Bivariate
======================================================

### Bivariate Analysis: User Type vs End Time
```{r, echo=FALSE}
bivariate_plot1
```

### Bivariate Analysis: User Type vs Location
```{r, echo=FALSE}
bivariate_plot2
```

### Bivariate Analysis: Charger Type vs Day of Week
```{r, echo=FALSE}
bivariate_plot3
```

### Bivariate Analysis: End Time vs Day of Week
```{r, echo=FALSE}
bivariate_plot4
```

Multivariate
======================================================

### Multivariate Analysis
```{r, echo=FALSE}
multivariate_plot
```
